### 2016-11-01 methodsPaper/tex/materialsAndMethods.tex
Added Approximation of Integral formula

As with the original ITHIM implementation we employed a comparative
risk analysis (CRA) across scenarios defined by mean active
transportation time, i.e., walking and cycling.

We compute the proportional change in national disease burden between
the baseline model and alternative scenarios, or population
attributable fraction, $\af$.  The population attributable fraction is
defined below, and computed for each disease included in the model,
namely Breast Cancer, Colon Cancer, Depression, Dementia, Diabetes and
Cardiovascular disease.

@@

>>>>

As with the original ITHIM implementation we employed a comparative
risk analysis (CRA) across scenarios defined by mean active
transportation time, i.e., walking and cycling.  To do so we
investigate the proportional change in national disease burden between
the baseline model and a given alternative scenario, i.e., the
population attributable fraction, $\af$.  The population attributable
fraction is defined below and computed for each disease included in
the model, namely Breast Cancer, Colon Cancer, Depression, Dementia,
Diabetes and Cardiovascular disease.

@@

\paragraph{Approximation of $\af$ Integral}

\begin{equation}
1 - \af \approx \frac{\sum R(x_i)}{\sum R(x_i^\prime)}
\end{equation}
